---
title: "Units_Exploration"
author: "Vinny Paris"
date: "4/15/2021"
output: html_document
---
# Residential Units
So to me there appears to be two different models happening. The first is everything up to about 4ish where there is a slow but steady gain. After that though the price seems to become pretty much a flat line for the extremely large values of the residential units. I think I know why too.
```{r, echo = FALSE}
data <- read.csv('../data/Queens Training Set.csv')
plot(log(data$RESIDENTIAL.UNITS + 1), log(data$SALE.PRICE + 1),
     xlab = 'Log of Res. Units + 1', ylab = 'Log of Sales Price + 1')
```

To fit it I used a basic LM where everything before 3.77 was fit with one intercept and slope on log(res_units + 1) and then a secondary intercept and slope for everything past 3.77

```{r, echo = FALSE}
my_cutter <- function(my_cut){
  k <- log(data$RESIDENTIAL.UNITS + 1) > my_cut
  moddy <- lm(log(SALE.PRICE + 1) ~ 0 + k + 
              log(1 + RESIDENTIAL.UNITS):k, data = data)
  return(sum(residuals(moddy)^2))
}
#Optim is okay but I figure we might as well just find the min 
#optim(4, my_cutter, method = 'Brent', lower = 3, upper = 5)
x <- seq(3, 5, .01)
my_cuts <- apply(data.frame(x), 1, my_cutter)
cat('SEL with a single mean only: ', sum(resid(lm(log(SALE.PRICE + 1) ~ 
              1, data = data))^2))
cat('SEL with basic LM: ', sum(resid(lm(log(SALE.PRICE + 1) ~ 
              log(1 + RESIDENTIAL.UNITS), data = data))^2))
cat('SEL with LM on each side of cutoff point: ', min(my_cuts))
cat('Optimal Cutoff Point: ', x[which.min(my_cuts)])
plot(x, my_cuts, xlab = 'Proposed cut off point',
     ylab = 'SEL')

```



# Total and Commercial units
I do not believe that Total Units or Commercial units are that important. The variance of the commercial units is interesting but I don't think it matters all that much if we just want to estimate means. 
```{r, echo = FALSE}
plot((data$COMMERCIAL.UNITS + 0), log(data$SALE.PRICE + 1))
plot(log(data$COMMERCIAL.UNITS + 1), log(data$SALE.PRICE + 1))
plot((data$TOTAL.UNITS + 0), log(data$SALE.PRICE + 1))
plot(log(data$TOTAL.UNITS + 1), log(data$SALE.PRICE + 1))
```



# Odd extreme values
I think I know what is happening. As for the massive units they all appear to be coops. So those whole areas appear to be giant co-ops (for example in the 3 buildings with the same largest gross square footage is a co-op with apparently two large apartment buildings and a lot of condos/townhouses from my googling). Anyway, these people who own an apartment/house in the co-op sell and  occasionally information is listed with the co-op statistics (ie you bought a condo with 1200 sqft of living space but since you bought into the co-op its posted as the total living area in the entire co-op.)



```{r, echo = FALSE}
head(data[order(data$RESIDENTIAL.UNITS, decreasing = TRUE),], 3)
```